Sustained software development, not number of citations or journal choice, is indicative of accurate bioinformatic software

### 2021-08-19 manuscript/manuscript-speed-accuracy.tex
Added Luis to the Acknowledgements, started describing additional features.

For each of the publications describing these tools, we have (where
possible) collected the journal's H5-index (
%\href{https://scholar.google.co.nz/citations?view\_op=top\_venues\&hl=en}{
Google Scholar Metrics
%}
), the maximum H-index and
corresponding M-indices \cite{Hirsch2005-mt} for the corresponding
authors for each tool, and the number of times the publication(s)
associated with a tool has been cited using Google Scholar (data
collected over a 6 month period in late 2020). Note that citation metrics
are not static and will change over time. In addition, where possible we also extract the version number, the number
of commits and number of contributors from GitHub repositories.

We have computed the Spearman’s correlation coefficient for each
pairwise combination of the mean normalised accuracy and speed ranks,
with the year published, mean relative age (compared to software in the
same benchmarks), journal H5 metrics, the total number of citations,
the relative number of citations (compared to software in the same
benchmarks) and the maximum H- and corresponding M-indices for the corresponding
authors, version number, and numbers of commits and contributors.
The results are presented in Figure~\ref{fig:allfactors}A\&B. We find
significant associations between most of the citation-based metrics
(journal H5, citations, relative citations, H-index and
M-index). There is also a negative correlation between the year of
publication, the relative age and many of the citation-based metrics.

@@

\section*{Acknowledgements}
The authors acknowledge the valued contribution of invaluable
discussions with Anne-Laure Boulesteix, Shinichi Nakagawa, Suetonia
Palmer and Jason Tylianakis. Murray Cox, Raquel
Norel, Alexandros Stamatakis, Jens Stoye,Tandy Warnow, provided
valuable feedback on drafts of the manuscript.

>>>>

For each of the publications describing these tools, we have (where
possible) collected the journal's H5-index (
%\href{https://scholar.google.co.nz/citations?view\_op=top\_venues\&hl=en}{
Google Scholar Metrics
%}
), the maximum H-index and
corresponding M-indices \cite{Hirsch2005-mt} for the corresponding
authors for each tool, and the number of times the publication(s)
associated with a tool has been cited using Google Scholar (data
collected over a 6 month period in late 2020). Note that citation metrics
are not static and will change over time. In addition, where possible we also extract the version number, the number
of commits, number of contributors
{\color{red} total number ``issues'', the proportion of issues that remain open, the number of pull requests, and the number of times the code was forked}
from public GitHub repositories.

We have computed the Spearman’s correlation coefficient for each
pairwise combination of the mean normalised accuracy and speed ranks,
with the year published, mean relative age (compared to software in the
same benchmarks), journal H5 metrics, the total number of citations,
the relative number of citations (compared to software in the same
benchmarks) and the maximum H- and corresponding M-indices for the corresponding
authors, version number,
{\color{red}and the GitHub statistics commits, contributors, pull requests, issues, \% open issues and forks}.
The results are presented in Figure~\ref{fig:allfactors}A\&B and S5\&S6. We find
significant associations between most of the citation-based metrics
(journal H5, citations, relative citations, H-index and
M-index). There is also a negative correlation between the year of
publication, the relative age and many of the citation-based metrics.

@@

\section*{Acknowledgements}
The authors acknowledge the valued contribution of invaluable
discussions with Anne-Laure Boulesteix, Shinichi Nakagawa, Suetonia
Palmer and Jason Tylianakis. Murray Cox, Raquel
Norel, Alexandros Stamatakis, Jens Stoye, Tandy Warnow, and 
Luis Pedro Coelho provided
valuable feedback on drafts of the manuscript.
